%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper]{developercv} % Default font size, values from 8-12pt are recommended

\usepackage{enumitem}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Ali Torabi}}}}}
	\\
	\vspace{6pt}
	\\
	{\huge Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Prague, Czechia}\\
	\icon{Phone}{12}{\href{tel:+420774053595}{+420 774 053 595}}\\
	\icon{At}{12}{\href{mailto:alitorabi2020@gmail.com}{\small alitorabi2020@gmail.com}}\\
\end{minipage}
\begin{minipage}[t]{0.25\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/torabi-ali}{@torabi-ali}}\\
	\icon{Github}{12}{\href{https://github.com/torabi-ali}{@torabi-ali}}\\
	\icon{PaperPlane}{12}{\href{https://t.me/torabi\_ali}{@torabi\_ali}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.55\textwidth} % 35% of the page width for the introduction text
	\cvsect{Who Am I?}
	\par
	Hello, I am Ali Torabi, a senior software engineer. I have been working on web, desktop and console applications using various technologies for the past 7 years. I enjoy creating innovative solutions that help solve real-world problems and make a positive impact on people’s lives. I am also keen on learning more about low-level programming and cloud computing.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.4\textwidth} % 50% of the page for the skills bar chart
	\cvsect{Skills}
	\begin{itemize}[noitemsep]
		\item Software Design
		\item Database Design
		\item Data Structure
		\item Design Patterns
	\end{itemize}
        \begin{itemize}[noitemsep]
		\item C\# \& .NET \& SQL
		\item TypeScript \& Vue.js
		\item C/C++ \& Python
		\item Azure \& AWS
	\end{itemize}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\vspace{\baselineskip}

\cvsect{Experience}
\begin{entrylist}
	\entry
	{2023 -- Present}
	{Full Stack .NET Developer}
	{\href{https://firstlinesoftware.com/}{First Line Software}}
	{I am a software engineer working on a large E-Commerce/CMS solution named Optimizely. The main challenges are:
	\begin{itemize}[noitemsep]
		\item Adding complex features to project regarding the requirements.
		\item Adding many useful reports for admin section.
		\item Adding SPA support to an existing project.
	\end{itemize}
	I learned the necessary skills for the project in a short time and started to write code that met the standards.
		\\\texttt{ASP.NET Core}\slashsep\texttt{SQL Server}\slashsep\texttt{Vue.js}\slashsep\texttt{ElasticSearch}}
	\entry
	{2020 -- 2023}
	{Full Stack .NET Developer}
	{\href{https://gooshishop.com}{Gooshishop - Hasin Technology.}}
	{I was a software engineer working on a large legacy E-Commerce solution. The main challenges were:
	\begin{itemize}[noitemsep]
		\item Maintaining project and fixing numerous bugs and issues.
		\item Optimizing many actions and easing the sales process.
		\item Choosing NopCommerce as base solution and implementing our needs in that.
		\item Migrating the whole system to new product.
	\end{itemize}
	I'm proud to say I improved some actions up to 60\% and Added so many features in years.
		\\\texttt{ASP.NET MVC}\slashsep\texttt{ASP.NET Core}\slashsep\texttt{SQL Server}\slashsep\texttt{PostgreSQL}\slashsep\texttt{ElasticSearch}}
	\entry
	{2020 -- 2020}
	{Part-Time Full Stack .NET Developer}
	{\href{https://itelemed.ca}{iTelemed - Canada Telemedicine Group Inc.}}
	{I was a part-time Full Stack .NET Developer on a fully online medical solution. Main challenges were:
	\begin{itemize}[noitemsep]
		\item Developing the project as fast as possible because of the Covid-19 situation.
		\item Preparing system to execute more than 100 complex requests in a minute.
		\item Reaching an architecture to enable us to scale the project.
	\end{itemize}
	Online visiting (video chat), text chat, ticketing and managing patients were some of features built in a 3 month work.
		\\\texttt{ASP.NET Core}\slashsep\texttt{SQL Server}\slashsep\texttt{SignalR}\slashsep\texttt{WebRTC}}
	\entry
	{2019 -- 2021}
	{Full Stack .NET Developer}
	{Algorithm Pars.}
	{I was a senior developer working on a legacy project which was widely in use in large companies. The main challenges were:
	\begin{itemize}[noitemsep]
		\item Reducing the expenses of maintaining the project.
		\item Creating a transition phase in order to migrate to .NET Core
		\item Creating and implementing a new framework to switch to ASP.NET Core.
            \item Reading and rewriting many parts of code and reduce line of code by 20\%.
	\end{itemize}
	I was a key person in this project and had a good collaboration with project manager. We have improved the performance more than 15\% through years.
		\\\texttt{ASP.NET Core}\slashsep\texttt{ASP.NET WebForms}\slashsep\texttt{SQL Server}}
	\entry
	{2018 -- 2019}
	{Software Consultant \& SEO Manager}
	{Sunseir Travel Agency}
	{Working with my nice colleagues on a website that implements both B2B and B2C business models which handles a very high amount of request. Also improving "Sunseir" brand, advertising and SEO on aside.
		\\\texttt{ASP.NET Core}\slashsep\texttt{SEO Tools}}
	\entry
	{2017 -- 2019}
	{.NET Developer}
	{Dipeh.ir}
	{Dipeh is a website to explore about books, authors and publishers. The main goal in this project was designing a software with very specified requirements Another important goal was reaching nice performance through maximum code optimization.
		\\\texttt{ASP.NET MVC}\slashsep\texttt{SQL Server}\slashsep\texttt{Bootstrap}}
	\entry
	{2016 -- 2018}
	{Junior Developer \& SEO Manager}
	{Mehr -o- Mah Travel Agency}
	{This was my first official job as developer. It was a large-scale app with lot's of functionalities that brightened me to professional programming.
		\\\texttt{ASP.NET MVC}\slashsep\texttt{SQL Server}\slashsep\texttt{Bootstrap}\slashsep\texttt{SEO Tools}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}
\begin{entrylist}
	\entry
	{2016 -- 2018}
	{Master's Degree}
	{Islamic Azad University, Najafabad, Iran}
	{I focused on software engineering and software development during MS and therefore my thesis was about predicting software bugs and defects early during development}
	\entry
	{2012 -- 2016}
	{Bachelor's Degree}
	{Zanjan University, Zanjan, Iran}
	{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\cvsect{Languages}
\begin{itemize}
	\setlength\itemsep{3px}
	\item \textbf{Persian} - Native
	\item \textbf{English} - Proficient
    \item \textbf{Czech} - Basic
\end{itemize}

\end{document}