%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Ali}}}}} % First name

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Torabi}}}}} % Last name

	\vspace{6pt}

	{\huge Senior .NET Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Tehran, Iran}\\
	\icon{Phone}{12}{\href{tel:+989137370539}{+98 913 737 0539}}\\
	\icon{At}{12}{\href{mailto:alitorabi2020@gmail.com}{\small alitorabi2020@gmail.com}}\\
\end{minipage}
\begin{minipage}[t]{0.25\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/torabi-ali}{@torabi-ali}}\\
	\icon{Github}{12}{\href{https://github.com/torabi-ali}{@torabi-ali}}\\
	\icon{PaperPlane}{12}{\href{https://t.me/torabi\_ali}{@torabi\_ali}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	Experienced .NET web programmer with a demonstrated history of working in the computer software industry. Skilled in C\#, .NET Core, ASP.NET MVC, ASP.NET WebForm and Windws applications. I love to design code and database, write complex queries, optimizing software systems and cleaning code.
	\\\vskip 3mm

	Studied Master of Science (MS) focused on Computer Software Engineering at Islamic Azad University, Najafabad Branch.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{6}
		\baritem{C\#}{95}
		\baritem{.NET Core}{90}
		\baritem{ASP.NET MVC}{90}
		\baritem{ASP.NET WebForms}{70}
		\baritem{WPF \& Windows Form}{50}
		\baritem{Design Patterns}{50}
		\baritem{Architecture}{70}
		\baritem{Microsoft SQL Server}{70}
		\baritem{PostgreSql}{60}
		\baritem{Redis}{60}
		\baritem{Docker}{50}
		\baritem{Git / TFS}{90}
		\baritem{Linux}{50}
		\baritem{C / C++}{50}
		\baritem{Python}{40}
		\baritem{Html, Css, Js}{60}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{6/\scriptsize{Problem Solving},4/\scriptsize{Creativity},6/\scriptsize{Team Player},5/\scriptsize{Fast Learning}}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
	{2020 -- Current}
	{Senior Full Stack Developer}
	{\href{https://gooshishop.com}{Gooshishop - Hasin Technology.}}
	{I am a senior full stack developer working on a large E-Commerce solution. My job there is mostly maintaining the project, bug fix, optimizing and documenting the solution. I'm proud to say I have improved some actions up to 70\% and Added so many features on my first year. Also I was a key person in migration process to ASP.NET Core.
		\\\texttt{ASP.NET MVC}\slashsep\texttt{ASP.NET Core}\slashsep\texttt{SQL Server}\slashsep\texttt{ElasticSearch}}
	\entry
	{2019 -- 2021}
	{Senior Back End Developer}
	{\href{https://apdp.ir}{Algorithm Pars.}}
	{I was a senior developer in this company working on a huge legacy project and preparing a new framework to migrate from Web Form to ASP.NET Core. The main challenge in this legacy application was to keep it up with business needs and remove codes where it was not needed and minify changing costs. Also there was challenges in migration process such as designing an architecture and using right design patterns to produce a long life, easy to modify and scalable website.
		\\\texttt{ASP.NET Core}\slashsep\texttt{ASP.NET WebForms}\slashsep\texttt{SQL Server}}
	\entry
	{2020 -- 2020}
	{Part-Time Senior Full Stack Developer}
	{\href{https://itelemed.ca}{iTelemed - Canada Telemedicine Group Inc.}}
	{I was a part-time senior full stack developer in this company working on a fully online medical solution. Online visiting (video chat), text chat, ticketing and managing patients were some of features built in a 3 month work.
		\\\texttt{ASP.NET Core}\slashsep\texttt{SQL Server}\slashsep\texttt{SignalR}}
	\entry
	{2018 -- 2018}
	{Developer}
	{SMS Management System}
	{This was a small app at the beginning to send, receive and manage messages between Sunseir company and it's customers. After all, it can manage different SMS providers and can send pre defined messages.
		\\\texttt{WPF}\slashsep\texttt{MVVM}\slashsep\texttt{Web API}}
	\entry
	{2018 -- 2019}
	{Software Consultant \& SEO Manager}
	{Sunseir Travel Agency}
	{Working with my nice colleagues on a website that implements both B2B and B2C business models which handles a very high amount of request. Also working on Sunseir brand, advertising and SEO on aside.
		\\\texttt{ASP.NET Core}\slashsep\texttt{SEO Tools}}
	\entry
	{2017 -- 2019\\\footnotesize{Freelance}}
	{.Net Developer}
	{Dipeh.ir}
	{Dipeh is a website to explore about books, authors and publishers. The main goal in this project was designing a software with very specified requirements Another important goal was reaching nice performance through maximum code optimization.
		\\\texttt{ASP.NET MVC}\slashsep\texttt{SQL Server}\slashsep\texttt{Bootstrap}}
	\entry
	{2016 -- 2018}
	{Junior Developer \& SEO Manager}
	{Mehr -o- Mah Travel Agency}
	{This was my first official job as developer. It was a large-scale app with lot's of functionalities that brightened me to professional programming.
		\\\texttt{ASP.NET MVC}\slashsep\texttt{SQL Server}\slashsep\texttt{Bootstrap}\slashsep\texttt{SEO Tools}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
	{2016 -- 2018}
	{Master's Degree}
	{Islamic Azad University, Najafabad Branch}
	{I focused on software engineering and software development during MS and therefore my thesis was about predicting software bugs and defects early during development}
	\entry
	{2012 -- 2016}
	{Bachelor's Degree}
	{Zanjan University}
	{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\cvsect{Languages}
\begin{itemize}
	\setlength\itemsep{3px}
	\item \textbf{Persian} - Native
	\item \textbf{English} - Proficient
\end{itemize}

%----------------------------------------------------------------------------------------

\cvsect{Hobbies}
\begin{itemize}
	\item Reading books and blogs
	\item Technology and psychology
	\item Teaching programming
	\item Walking and jogging
	\item Listening to music
	\item Watching movie
	\item Gardening
	\item Cooking
	\item Sharing information of any kind
\end{itemize}

%----------------------------------------------------------------------------------------

\end{document}